### 2015-04-28 ApTranscriptome_TR.Rmd
Changed figures of deviation from expectations to vertical orientation.

mh_plot_sub1 <- qplot(x=Apic, y=Acar, data=md_sub1, fill=value, geom="tile", ylim = rev(levels(md_sub1$Acar))) + 
  scale_fill_gradient2(limits=c(-700, 600), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(x = "A. picea", y = "A. carolinensis") +
  theme(legend.position = "none") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 1.5, ymax = 2.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 3.5, xmax = 4.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

mh_plot_sub2 <- qplot(x=Acar, y=Apic, data=md_sub2, fill=value, geom="tile", ylim = rev(levels(md_sub2$Apic))) + 
  scale_fill_gradient2(limits=c(-700, 600), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(x = "A. carolinensis", y = "A. picea") + 
  theme(legend.position = "bottom") + 
  geom_rect(xmin = 2.5, xmax = 3.5, ymin = 1.5, ymax = 2.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 3.5, xmax = 4.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

png("results/matched_observations_Fig2.png")
grid.arrange(mh_plot_sub1, mh_plot_sub2, ncol=1, heights = c(0.45, 0.6))
dev.off()

@@

The *enhanced defense hypothesis* posits that temperature adaptation uses existing defense mechanisms, which should result in significant overlap in response. This pattern would be apparent as an excess of transcripts with the same response pattern between species (e.g. more shared "Low" transcripts) and a deficit of transcripts that shift to other response patterns or become not responsive.

@@

# plot
enhanced_defense_plot <- qplot(x=Apic, y=Acar, data=enhanced_defense_dat, fill=value, geom="tile", ylim = rev(levels(enhanced_defense_dat$Acar))) + 
  scale_fill_gradient2(limits=c(-500, 500), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(x = "A. picea", y = "A. carolinensis") +
  theme(legend.position = "none") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 1.5, ymax = 2.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 3.5, xmax = 4.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

# title
enhanced_defense_plot <- enhanced_defense_plot + ggtitle('Enhanced defense hypothesis') + theme(plot.title = element_text(hjust=0))
enhanced_defense_plot
```

@@

# plot
tolerance_plot <- qplot(x=Apic, y=Acar, data=tolerance_dat, fill=value, geom="tile", ylim = rev(levels(tolerance_dat$Acar))) + 
  scale_fill_gradient2(limits=c(-500, 500), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(x = "A. picea", y = "A. carolinensis") +
  theme(legend.position = "bottom") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 1.5, ymax = 2.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 3.5, xmax = 4.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

# plot together
png("results/predictions_Fig1.png")
grid.arrange(enhanced_defense_plot, tolerance_plot, ncol=1, heights = c(0.45, 0.6))
dev.off()
```

@@

plot(log(mean.exp[which(mean.exp$colony == "A22"), "mean.TPM"]), 
     log(mean.exp[which(mean.exp$colony == "Ar"), "mean.TPM"]))
```

@@

length(which(responsive.lms.ann.type$Transcript %in% annotation.table[which(annotation.table$best.hit.to.nr != "-"), "Sequence.Name"]))

best.hit.to.nr != "-")

>>>>

mh_plot_sub1 <- qplot(y=Apic, x=Acar, data=md_sub1, fill=value, geom="tile", xlim = rev(levels(md_sub1$Acar))) + 
  scale_fill_gradient2(limits=c(-700, 600), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(y = "A. picea", x = "A. carolinensis") +
  theme(legend.position = "none") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 3.5, ymax = 4.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 1.5, xmax = 2.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

mh_plot_sub2 <- qplot(y=Acar, x=Apic, data=md_sub2, fill=value, geom="tile", xlim = rev(levels(md_sub2$Apic))) + 
  scale_fill_gradient2(limits=c(-700, 600), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(y = "A. carolinensis", x = "A. picea") + 
  theme(legend.position = "right") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 3.5, ymax = 4.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 1.5, xmax = 2.5, ymin = 2.5, ymax = 3.5, fill = "transparent", linetype=2, colour="black")

@@

png("results/matched_observations_Fig2.png")
grid.arrange(mh_plot_sub1, mh_plot_sub2, ncol=2)
dev.off()

@@

The *enhanced response hypothesis* posits that temperature adaptation uses existing defense mechanisms, which should result in significant overlap in response. This pattern would be apparent as an excess of transcripts with the same response pattern between species (e.g. more shared "Low" transcripts) and a deficit of transcripts that shift to other response patterns or become not responsive.

@@

# plot
enhanced_defense_plot <- qplot(y=Apic, x=Acar, data=enhanced_defense_dat, fill=value, geom="tile", xlim = rev(levels(enhanced_defense_dat$Acar))) + 
  scale_fill_gradient2(limits=c(-500, 500), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(y = "A. picea", x = "A. carolinensis") +
  theme(legend.position = "none") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 3.5, ymax = 4.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 1.5, xmax = 2.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

# title
enhanced_defense_plot <- enhanced_defense_plot + ggtitle('Enhanced Response hypothesis') + theme(plot.title = element_text(hjust=0))
enhanced_defense_plot
```

@@

# plot
tolerance_plot <- qplot(y=Apic, x=Acar, data=tolerance_dat, fill=value, geom="tile", xlim = rev(levels(tolerance_dat$Acar))) + 
  scale_fill_gradient2(limits=c(-500, 500), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(y = "A. picea", x = "A. carolinensis") +
  theme(legend.position = "bottom") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 3.5, ymax = 4.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 1.5, xmax = 2.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

# plot together
png("results/predictions_Fig1.png")
grid.arrange(enhanced_defense_plot, tolerance_plot, ncol=2)
dev.off()
```

@@

plot(log(mean.exp[which(mean.exp$colony == "A22"), "mean.TPM"]), 
     log(mean.exp[which(mean.exp$colony == "Ar"), "mean.TPM"]),
     xlab = "log(expression) A. picea",
     ylab = "log(expression) A. carolinensis")
abline(a=0, b=1)
```

@@
